### 2023-02-26 manuscript.Rmd
Auto-formatting

```{r, eeg_processing, include=FALSE}
# Define function for processing behavioral log files
read_log <- function(log_file) {

  # Read the file
  log <- read_tsv(
    log_file,
    col_types = cols(),
    locale = locale(encoding = "latin1"),
    progress = FALSE
  ) %>%
    # Recode some columns
    transmute(

@@

# (Re-)do the actual preprocessing if requested
if (run$eeg_processing) {

  # Process behavioral data
  logs <- map(log_files, read_log)

@@

# Define helper function for fitting linear mixed models and computing contrasts
fit_mixed_models <- function(dep, formula, data) {

  # Modify the formula such that fixed effects are always retained
  formula <- formula %>%
    tabulate.formula() %>%
    mutate(block = replace(block, is.na(grouping), "fixed"))

@@

# (Re-)do the actual model fitting if requested
deps <- config$components$name
if (run$mixed_models) {

  # Fit the model for each ERP component
  form_erps <- ~ phase * condition +
    (phase * condition | participant_id) +
    (phase * condition | item_id)
  models <- map(deps, fit_mixed_models, formula = form_erps, data = trials) %>%
    set_names(deps)

@@

  # Save models
  saveRDS(models, here(output_dir, "models.RDS"))
} else {

  # Read fitted models
  models <- readRDS(here(output_dir, "models.RDS"))
}

>>>>

```{r, eeg_processing, include=FALSE}
# Define function for processing behavioral log files
read_log <- function(log_file) {
  # Read the file
  log <- read_tsv(
    log_file,
    col_types = cols(),
    locale = locale(encoding = "latin1"),
    progress = FALSE
  ) %>%
    # Recode some columns
    transmute(

@@

# (Re-)do the actual preprocessing if requested
if (run$eeg_processing) {
  # Process behavioral data
  logs <- map(log_files, read_log)

@@

# Define helper function for fitting linear mixed models and computing contrasts
fit_mixed_models <- function(dep, formula, data) {
  # Modify the formula such that fixed effects are always retained
  formula <- formula %>%
    tabulate.formula() %>%
    mutate(block = replace(block, is.na(grouping), "fixed"))

@@

# (Re-)do the actual model fitting if requested
deps <- config$components$name
if (run$mixed_models) {
  # Fit the model for each ERP component
  form_erps <- ~ phase * condition +
    (phase * condition | participant_id) +
    (phase * condition | item_id)
  models <- map(deps, fit_mixed_models, formula = form_erps, data = trials) %>%
    set_names(deps)

@@

  # Save models
  saveRDS(models, here(output_dir, "models.RDS"))
} else {
  # Read fitted models
  models <- readRDS(here(output_dir, "models.RDS"))
}
